LDATS Rodents Example

### 2019-07-04 doc/rodents-example.Rmd
elevating timename to a main argument
pulling it out of the TS controls list

We use `LDA_set()` to run replicate LDA models (each with its own seed) with varying numbers of topics (`2:6`) and `select_LDA()` to select the best model.

@@

```{r lda_set, eval =F}
lda_model_set <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:6),
                         nseeds = 100,
                        control = LDA_controls_list(quiet = TRUE))

@@

If we do not pass any controls, by default, `quiet = FALSE` (here run with only `2:3` topics and  `10` seeds, to keep output short):

```{r lda set not quiet}
lda_model_set2 <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:3),
                         nseeds = 10)
```

@@

```{r ts on lda, eval = F}
changepoint_models <- TS_on_LDA(LDA_models = selected_lda_model, 
                                document_covariate_table = rodents$document_covariate_table,
                                formulas = ~ sin_year + cos_year,
                                nchangepoints = c(0:6), 
                                weights = document_weights(rodents$document_term_table),
                                control = TS_controls_list(nit = 1000, timename = "newmoon"))

@@

Also, it is important to note that by default the TS functions take the name of the time-step column from the `document_covariate_table` to be `"time"`. To pass a different column name, use the `timename` argument in `TS_controls_list()`.

@@

```{r lda_ts, eval = F}
lda_ts_results <- LDA_TS(document_term_table = rodents$document_term_table,
                         document_covariate_table = rodents$document_covariate_table,
                         nseeds = 100, 
                         topics = 2:6,
                         formulas = ~ sin_year + cos_year,
                         nchangepoints= 0:6,
                         weights = document_weights(rodents$document_term_table),
                         control = LDA_TS_controls_list(
                           TS_control = TS_controls_list(nit = 1000, timename = "newmoon")))
```

@@

```{r plot LDA_TS results, fig.height = 16, fig.width = 7, echo = F}
plot(lda_ts_results, control = LDA_TS_controls_list(
                           TS_control = TS_controls_list(timename = "newmoon")))
```

>>>>

We use `LDA_set()` to run replicate LDA models (each with its own seed) with varying numbers of topics (`2:5`) and `select_LDA()` to select the best model.

@@

```{r lda_set, eval =F}
lda_model_set <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:5),
                         nseeds = 10,
                         control = LDA_controls_list(quiet = TRUE))

@@

If we do not pass any controls, by default, `quiet = FALSE` (here run with only `2:3` topics and `2` seeds, to keep output short):

```{r lda set not quiet}
lda_model_set2 <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:3),
                         nseeds = 2)
```

@@

```{r ts on lda, eval = F}
changepoint_models <- TS_on_LDA(LDA_models = selected_lda_model, 
                                document_covariate_table = rodents$document_covariate_table,
                                formulas = ~ sin_year + cos_year,
                                nchangepoints = c(0:1), 
                                weights = document_weights(rodents$document_term_table),
                                timename = "newmoon",
                                control = TS_controls_list(nit = 1000))

@@

Also, it is important to note that by default the TS functions take the name of the time-step column from the `document_covariate_table` to be `"time"`. To pass a different column name, use the `timename` argument in `TS_on_LDA()`.

@@

```{r lda_ts, eval = F}
lda_ts_results <- LDA_TS(document_term_table = rodents$document_term_table,
                         document_covariate_table = rodents$document_covariate_table,
                         nseeds = 10, 
                         topics = 2:5,
                         formulas = ~ sin_year + cos_year,
                         nchangepoints= 0:1,
                         weights = document_weights(rodents$document_term_table),
                         timename = "newmoon",
                         control = LDA_TS_controls_list(
                           TS_control = TS_controls_list(nit = 1000)))
```

@@

```{r plot LDA_TS results, fig.height = 16, fig.width = 7, echo = F}
plot(lda_ts_results)
```
